Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-24 products/manuscript/Manuscript.qmd
Project

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}

# 1)  working directory to the project root
setwd("C:/Users/ajose35/Desktop/MADA-course/Joseph-MADA-project")

# 2) Chunk defaults
knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE
)
```

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# Generate predicted probabilities over the range of gravidity
predicted_probs <- ggeffect(model_gravidity, terms = "gravidity")

# Create a scatter/line plot of predicted probabilities by gravidity
ggplot(predicted_probs, aes(x = x, y = predicted)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, fill = "blue") +
  labs(title = "",
       x = "Gravidity",
       y = "Predicted Probability") +
  theme_minimal()

>>>>

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics( here::here( "Images", "Figure 3. Predicted Probability of Adverse Outcome by Gravidity Age  25.png"
  )
)
